Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-12 paper/disc20clustering.tex
comments
The right insigths into generalizing LB

\medskip
\noindent
\textbf{Algorithmic techniques.} The variant for general $k$ is still unresolved, hence it is vital to summarize algorithmic techniques used in this paper.
A straightforward analysis of the algorithm from Section~\ref{sec:k3} results in the bound $O(\ell^2)$, and the analysis must be improved in two places. One must bound the cost of each of $O(\ell)$ reconfigurations in a phase by a~constant, and show that the optimum offline algorithm must pay for a significant portion of inter-cluster requests.
We bound the cost of the latter by estimating the capabilities of the optimum offline algorithm to \emph{prepare} for an incoming sequence of requests.
Furthermore, in the analysis of the algorithm from Section~\ref{sec:k2}, we propose a~novel charging scheme for edges that share a vertex.

@@

The ground sets constructed in this lower bound can be perfectly partitioned into the clusters (i.e., with nodes of each ground set collocated).
This way, the optimal algorithm moves to a perfect partition at the beginning (where requests incur the cost~$0$), thus its cost is bounded.
If the algorithm splits any pair of nodes of a ground set, the adversary issues requests to any pair of split nodes.
These two observations imply that the algorithm must eventually collocate all nodes of a~ground set to be competitive.

@@

>>>>

\medskip
\noindent
\textbf{Algorithmic techniques.} The variant for general $k$ is still unresolved, hence it is vital to summarize algorithmic techniques used in this paper.
A straightforward analysis of the algorithm from Section~\ref{sec:k3} results in the bound $O(\ell^2)$, and the analysis must be improved in two places. One must bound the cost of each of $O(\ell)$ reconfigurations in a phase by a~constant, and show that the optimum offline algorithm must pay for a significant portion of inter-cluster requests \maciek{how to concisely say that there is also a migrate possibilty}.
We bound the cost of the latter by estimating the capabilities of the optimum offline algorithm to \emph{prepare} for an incoming sequence of requests.
Furthermore, in the analysis of the algorithm from Section~\ref{sec:k2}, we propose a~novel charging scheme for edges that share a vertex.

@@

@@

\noindent
\textbf{Lower bound for the general problem.}
For a lower bound $\Omega(k\cdot \ell)$ for the general partitioning problem, the adversary continues to issue requests to split nodes of a ground set until the algorithm collocates them.
The ground sets constructed in our lower bound can be perfectly partitioned into the clusters.
This way, the optimal algorithm moves to a perfect partition at the beginning (where requests incur the cost~$0$), thus its cost is bounded.
If the algorithm splits any pair of nodes of a ground set, the adversary issues requests to any pair of split nodes.
These two observations imply that the algorithm must eventually collocate all nodes of a~ground set to be competitive.
The construction is oblivious to the choice of the reconfiguration cost $\alpha$: we compare the 	number of node exchanges of \ALG and \OPT.
